A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss From Powdery Mildew in Australian Mungbean

### 2020-08-04 paper/paper.Rmd
Wordsmithing and references for diseases in Oz mungs

The high variability in yields can in part be attributed to a range of diseases that affect the crop [@Wood1990; @Conde1991; @Fuhlbohm1996; @Fuhlbohm2013; @Wilson2001; @Noble2019].
Along with these bacterial, fungal and phytoplasma caused diseases, another fungal disease, powdery mildew, can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars. The disease is caused by  The damage can be mitigated through an integrated disease management strategy of fungicide treatments and cultural practices and loci conferring resistance in mungbean have been identified [@Zhang2008]. However, to date, the focus in Australia has remained on breeding for disease resistance to bacterial diseases rather than powdery mildew due to the wide availability of fungicides for use in controlling powdery mildew. <!-- Best to get a quote from Col here so we can say "personal comm". I've heard him say this at a mungbean field day, I believe. -->

>>>>

The high variability in yields can in part be attributed to a range of diseases that affect the crop [@Wood1990; @Conde1991; @Fuhlbohm1996; @Fuhlbohm2013; @Wilson2001; @Noble2019].
Along with these bacterial, fungal and phytoplasma caused diseases, another fungal disease, powdery mildew, can reduce yields by up to 40% [@Chankaew2013] in susceptible cultivars.
The disease in Australia currently is thought to be caused by *Podosphaera xanthii*, however, this description has changed over time and a second species has also been cited as causing the disease but not yet officially classified [@Kelly2019].
Other research refers to the causal agent as *Erysiphe polygoni* outside of Australia [@Thakur1995].

The damage can be mitigated through an integrated disease management strategy of fungicide treatments and cultural practices and loci conferring resistance in mungbean have been identified [@Humphry2003; @Zhang2008]. However, to date, the focus in Australia has remained on breeding for disease resistance to bacterial diseases rather than powdery mildew due to the wide availability of fungicides for use in controlling powdery mildew. <!-- Best to get a quote from Col here so we can say "personal comm". I've heard him say this at a mungbean field day, I believe. -->
